Comparing software variability across and within fMRI analysis packages

### 2022-01-03 paper/paper.tex
camille more comments

Table~\ref{table:pipeline-stats} presents summary statistics for variability in the
group-level t-statistics. For each tool pair (A, B), BT was
significantly larger than machine error in tool A or B, in both thresholded
and unthresholded maps (Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
% \gk{we don't have sufficient sample size to say that p is that small,
% so we should probably say less than $10^{-5}$ or something else we could actually
% arrive at with our number of repetitions, pipeline pairs, and samples.}
% for all tests, t-test p=0 \gk{similar comment re p value} for all tests) \camille{p is smaller than a very small p but not zero?}.
These global differences were confirmed by Bland-Altman plots showing a
clear dominance of BT over WT
(Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B}).
In addition, BT and WT appeared moderately correlated across voxels (Pearson's r
in [0.60, 0.62], p$< 10^{-5}$, Figure~\ref{fig:unthresh-maps}-\textbf{C}). 
% Interestingly, the correlation appears driven by a set of voxels exhibiting comparable BT and
% WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have
% any spatial consistency.

\setlength{\tabcolsep}{5pt}
\begin{table}[h]
  \centering
  \begin{tabular}{cccccc|cc}
    \toprule
                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
    % \cmidrule{3-8}
    {}                & {}           & $\mu$                           & $\sigma$                           & $\mu$                             & $\sigma$ & $\mu$ & $\sigma$ \\
    \midrule
    \rowcolor{lightgray!50}
    {Between Tools}   & FSL vs. SPM  & 2.564                           & 1.050                              & 0.887                             & 0.689    & 0.733 & 0.586    \\
    \rowcolor{lightgray!50}
    {(BT)}            & FSL vs. AFNI & 3.096                           & 1.232                              & 1.095                             & 0.882    & 0.878 & 0.704    \\
    \rowcolor{lightgray!50}
    {}                & AFNI vs. SPM & 2.951                           & 1.344                              & 1.218                             & 0.955    & 0.983 & 0.762    \\
    {Within Tool}     & FSL          & 0.510                           & 0.697                              & 0.127                             & 0.098    & 0.120 & 0.083    \\
    {(WT)}            & SPM          & 0.367                           & 0.638                              & 0.085                             & 0.068    & 0.075 & 0.056    \\
    {}                & AFNI         & 0.637                           & 0.747                              & 0.199                             & 0.202    & 0.167 & 0.197    \\
    \bottomrule
  \end{tabular}
  \caption{Voxel-wise mean and standard deviation of BT and WT variability
    in t-statistics maps.}
  \label{table:pipeline-stats}
\end{table}

@@

Table~\ref{table:pipeline-stats} also presents summary statistics for
subject-level unthresholded t-statistics maps. As for group-level maps,
BT was consistently larger than WT (Wilcoxon
signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
However, for
some subjects and for AFNI, WT approached 
BT in some regions (Figure~\ref{fig:unthresh-maps-sbj}). As for the group maps, BT and WT
 appeared moderately correlated for all subjects (r in [0.484,
    0.633], p$< 10^{-5}$ for all subjects, see Supplemental Material~\ref{sec:supp-subjects} and~\ref{sec:supp-worst-subject}).

@@

Figure~\ref{fig:unthresh-correlation-allsbj} plots the relationship between
WT and BT for each subject, showing a consistent moderate correlation between BT and
WT.

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/5-marked.pdf}
  % \includegraphics[width=\textwidth]{figures/plots/wt-tstats/5-framed.png}
  % \includegraphics[width=.6\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
  \caption{For subject with highest WT variability, unthresholded subject-level t-statistics
  within tools at machine error for FSL (\textbf{A}),
  SPM (\textbf{B}), AFNI (\textbf{C}).}
  \label{fig:unthresh-worst-sbj}
\end{figure*}

>>>>

Table~\ref{table:pipeline-stats} presents summary statistics for variability in the
group-level t-statistics. For each tool pair (A, B), BT \camille{could we restate which metric we are looking at here -- as it stands BT means between-tool but coul represent many different metrics? It is ``absolute difference BT''?} was
significantly larger than machine error in tool A or B, in both thresholded
and unthresholded maps (Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
% \gk{we don't have sufficient sample size to say that p is that small,
% so we should probably say less than $10^{-5}$ or something else we could actually
% arrive at with our number of repetitions, pipeline pairs, and samples.}
% for all tests, t-test p=0 \gk{similar comment re p value} for all tests) \camille{p is smaller than a very small p but not zero?}.
These global differences were confirmed by Bland-Altman plots showing a
clear dominance of BT over WT
(Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B}).
In addition, BT and WT appeared moderately correlated across voxels (Pearson's r
in [0.60, 0.62], p$< 10^{-5}$, Figure~\ref{fig:unthresh-maps}-\textbf{C}). 
% Interestingly, the correlation appears driven by a set of voxels exhibiting comparable BT and
% WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have
% any spatial consistency.

\setlength{\tabcolsep}{5pt}
\begin{table}[h]
  \centering
  \begin{tabular}{cccccc|cc}
    \toprule
                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
    % \cmidrule{3-8}
    {}                & {}           & $\mu$                           & $\sigma$                           & $\mu$                             & $\sigma$ & $\mu$ & $\sigma$ \\
    \midrule
    \rowcolor{lightgray!50}
    {Between Tools}   & FSL vs. SPM  & 2.564                           & 1.050                              & 0.887                             & 0.689    & 0.733 & 0.586    \\
    \rowcolor{lightgray!50}
    {(BT)}            & FSL vs. AFNI & 3.096                           & 1.232                              & 1.095                             & 0.882    & 0.878 & 0.704    \\
    \rowcolor{lightgray!50}
    {}                & AFNI vs. SPM & 2.951                           & 1.344                              & 1.218                             & 0.955    & 0.983 & 0.762    \\
    {Within Tool}     & FSL          & 0.510                           & 0.697                              & 0.127                             & 0.098    & 0.120 & 0.083    \\
    {(WT)}            & SPM          & 0.367                           & 0.638                              & 0.085                             & 0.068    & 0.075 & 0.056    \\
    {}                & AFNI         & 0.637                           & 0.747                              & 0.199                             & 0.202    & 0.167 & 0.197    \\
    \bottomrule
  \end{tabular}
  \caption{Voxel-wise mean and standard deviation of BT and WT variability
    in t-statistics maps \camille{here and in other places -- is it t-statistic maps? (i.e. without s after statistic)}.}
  \label{table:pipeline-stats}
\end{table}

@@

Table~\ref{table:pipeline-stats} also presents summary statistics for
subject-level unthresholded t-statistics maps \camille{Is this for one subject in particular ? If so how was it chosen ?Or a mean over all subjects?}. As for group-level maps,
BT was consistently larger than WT (Wilcoxon
signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
However, for
some subjects and for AFNI, WT approached 
BT in some regions (Figure~\ref{fig:unthresh-maps-sbj}). As for the group maps, BT and WT
 appeared moderately correlated for all subjects (r in [0.484,
    0.633], p$< 10^{-5}$ for all subjects, see Supplemental Material~\ref{sec:supp-subjects} and~\ref{sec:supp-worst-subject}).

@@

Figure~\ref{fig:unthresh-correlation-allsbj} plots the relationship between
WT and BT for each subject \camille{across voxels?}, showing a consistent moderate correlation between BT and
WT.

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/5-marked.pdf}
  % \includegraphics[width=\textwidth]{figures/plots/wt-tstats/5-framed.png}
  % \includegraphics[width=.6\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
  \caption{For subject with highest WT variability, unthresholded subject-level t-statistics
  within tools at machine error for FSL (\textbf{A}),
  SPM (\textbf{B}), AFNI (\textbf{C}). \camille{If I understand correctly the point you are making here is that WT(AFNI) at some voxels is close to AFNI-SPM ? What is surprising here for me is that WT(AFNI) seems to be quite different from WT(SPM) and WT(FSL). Do we have a good idea why? Maybe looking at the maps would help?} }
  \label{fig:unthresh-worst-sbj}
\end{figure*}
